%-------------------------
% Resume in LaTeX
% Based on Professional ATS-Friendly Format
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Priyal Jain} \\ \vspace{1pt}
    \small +1(206) 530-9242 $|$ \href{mailto:priyaljainaux@gmail.com}{\underline{priyaljainaux@gmail.com}} $|$ 
    \href{https://www.linkedin.com/in/priyal-jain-72246919a/}{\underline{https://www.linkedin.com/in/priyal-jain-72246919a/}} $|$
    Seattle, WA
\end{center}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Washington}{Seattle, WA}
      {Master of Science in Data Science}{Sep. 2025 -- Mar. 2027}
    \resumeSubheading
      {Vellore Institute of Technology}{Amaravati, India}
      {B.Tech. in Computer Science and Engineering (Data Analytics Specialization)}{Jul. 2019 -- Jul. 2023}
  \resumeSubHeadingListEnd



%-----------LEADERSHIP & VOLUNTEER EXPERIENCE-----------
\section{Leadership \& Volunteer Experience}
  \resumeSubHeadingListStart
  
    \resumeSubheading
      {Vice President}{2020 -- 2021}
      {RUDRA NGO Club, Vellore Institute of Technology}{}
      \resumeItemListStart
        \resumeItem{Led team of 50+ volunteers in organizing community service initiatives, demonstrating strong customer service orientation and ability to work with diverse groups.}
        \resumeItem{Managed club operations, scheduling, and strategic planning while coordinating partnerships with local organizations.}
        \resumeItem{Developed training programs for new volunteers, showcasing ability to explain procedures clearly and work collaboratively.}
      \resumeItemListEnd

    \resumeSubheading
      {Member, Corporate Social Responsibility (CSR) Community}{2023 -- 2025}
      {Bosch Global Software Technologies}{}
      \resumeItemListStart
        \resumeItem{Contributed to development of educational materials for visually impaired students, demonstrating commitment to serving diverse user groups and fostering inclusivity.}
      \resumeItemListEnd

    \resumeSubheading
      {Minister for Conservation and Preservation}{2015 (7 years total)}
      {Junior Red Cross (JRC), Grades 6--12}{}
      \resumeItemListStart
        \resumeItem{Led educational workshops, organized donation drives, and coordinated community service initiatives over seven years, demonstrating reliability and long-term commitment.}
        \resumeItem{Managed logistics for multiple simultaneous projects including disaster relief, health education, and children's welfare programs.}
        \resumeItem{Honored with 'Best JRCian' award at district and state level for exceptional service commitment and leadership.}
      \resumeItemListEnd

    \resumeSubheading
      {Core Committee Member \& Documentation Lead}{2019}
      {VITOPIA Cultural Fest, VIT}{}
      \resumeItemListStart
        \resumeItem{Selected as one of only two freshers for core committee position among 100+ applicants, demonstrating strong work ethic and quick adaptability.}
        \resumeItem{Coordinated logistics and maintained detailed documentation for university's flagship cultural festival serving diverse student population.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------SKILLS-----------
\section{Skills \& Competencies}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Customer Service}{: Strong interpersonal communication, conflict resolution, working with diverse populations, training and mentoring} \\
     \textbf{Organizational Skills}{: Detail-oriented, record keeping, multi-tasking, time management} \\
     \textbf{Communication}{: Public speaking, written communication, explaining complex procedures clearly, phone etiquette} \\
     \textbf{Work Attributes}{: Quick learner, independent worker, reliable attendance, flexible availability, team collaboration, Microsoft Suite} \\
     \textbf{Technical}{: Proficient with computer systems, Canva/Figma/Adobe for creative presentations, systematic organization methods, statistical record-keeping}
    }}
 \end{itemize}

%-----------AWARDS-----------
\section{Awards \& Recognition}
    \begin{itemize}[leftmargin=0.15in, label={}]
        \small{\item{
            \textbf{Growth Driver Award} - Bosch Global Software Technologies (2024): Recognized for successful project completion and leadership \\
            \textbf{Best JRCian Award} - District and State Level (2015): Junior Red Cross recognition for exceptional community service \\
            \textbf{Best Prefect Award} - School Dean for Girls (2018): Outstanding leadership and community service as head girl \\
            \textbf{Competition Recognition}: Multiple victories in public speaking, essay writing, and debate competitions
        }}
    \end{itemize}

%-------------------------------------------
\end{document}